---
title: "Vignette Title"
author: "Takayuki Kaisen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Vignette Info

This vignette shows how to use gsedr library. In this library, you can generate a plot as a time-line and a map with data from [The Significant Earthquake Database](https://www.ngdc.noaa.gov/nndc/struts/form?t=101650&s=1&d=1).


## How to install

```{r setup, include=FALSE}
install.packages("devtools")
library(devtools)
install_github("https://github.com/ksnt/gsedr")
```

## Retrieve and Tidy Data

Use `eq_clean_data` function.(`eq_location_clean` function is used in this function)  

```{r "eq_clean_data", eval=FALSE}
# Retrieve earthquake data after 2000 a.c. in Mexico 
datapath <- system.file("extdata", "earthquakes.txt", package = "gsedr")
after2000data <- readr::read_delim(datapath, delim = "\t") %>% eq_clean_data()  %>% dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000)
```

## Create Timeline

Use `geom_timeline_label` function.

```{r "geom_timeline_label", eval=FALSE}
# Retrieve earthquake data after 1900 in JAPAN, TURKEY, HAITI, and INDONESIA.
# Create time-line plot

datapath <- system.file("extdata", "earthquakes.txt", package = "gsedr")
data <- readr::read_delim(datapath, delim = "\t") %>% eq_clean_data()
ddd <- data %>% dplyr::filter(COUNTRY %in% c('USA', 'JAPAN','TURKEY','HAITI','INDONESIA')) %>% dplyr::filter(!is.na(EQ_PRIMARY), !is.na(DEATHS)) %>% dplyr::filter(YEAR > 1900)
ddd %>% ggplot(aes(x=DATE,y=COUNTRY,size=as.numeric(EQ_PRIMARY),colour=as.numeric(TOTAL_DEATHS))) + geom_point(alpha=0.6) + geom_timeline_label(aes(label = LOCATION_NAME), n_max = 3) + scale_colour_gradient(low="skyblue",high = "red") + annotate("text", label = "ship", parse=TRUE) + labs(size = "Richter scale value", color = "# deaths") + theme_minimal()
```

## Create Map

Use `eq_create_label` function and `eq_map` function.


```{r "eq_create_label", eval=FALSE}
# Retrieve earthquake data in INDONESIA.
# Create a map with data

datapath <- system.file("extdata", "earthquakes.txt", package = "gsedr")
data <- readr::read_delim(datapath, delim = "\t") %>% eq_clean_data()
dddd <- data %>% dplyr::filter(COUNTRY %in% c('INDONESIA')) %>% dplyr::filter(!is.na(EQ_PRIMARY), !is.na(DEATHS))
dddd %>% dplyr::mutate(popup_text = eq_create_label(.)) %>% eq_map(annot_col = "popup_text")
```
